Semantic Preserving Bijective Mappings for Expressions involving Special Functions between Computer Algebra Systems and Document Preparation Systems

### 2018-11-30 main.tex
Consistently marked appropriate, inappropriate, and direct in italic (close #28)

{\sloppy The overall forward translation process is explained in~\Cref{fig:forward-trans}. All translation patterns and related information are stored in the DLMF/DRMF tables. These tables are converted by the \verb|lexicon-creator| to the \verb|DLMF-macros-lexicon| lexicon file. Together with the \verb|global|-\verb|lexicon| file, the \gls*{pom-pt} will be created by the \gls*{pom}-tagger. The \verb|latex-converter| takes a string representation of a semantic \LaTeX{} expression and uses the \gls*{pom} engine as well as our \verb|Translator| to create an appropriate string representation for a specified \gls*{cas}.}

>>>>

{\sloppy The overall forward translation process is explained in~\Cref{fig:forward-trans}. All translation patterns and related information are stored in the DLMF/DRMF tables. These tables are converted by the \verb|lexicon-creator| to the \verb|DLMF-macros-lexicon| lexicon file. Together with the \verb|global|-\verb|lexicon| file, the \gls*{pom-pt} will be created by the \gls*{pom}-tagger. The \verb|latex-converter| takes a string representation of a semantic \LaTeX{} expression and uses the \gls*{pom} engine as well as our \verb|Translator| to create a proper string representation for a specified \gls*{cas}.}
